Kindly Bent to Free Us

### 2019-07-11 kindly/infer/infer.tex
Small patch to the soundness theorem.

\begin{theorem}[Soundness of inference]
  Given a type environment $\E$ and a term $e$,\\
  if $\inferW{\Sv}{(C,\unif)}{\E}{e}{\tau}$
  then $\inferS{C}{\unif\Sv}{e}{\tau}$, $\unif C = C$ and $\unif \tau = \tau$.
\end{theorem}

Note here that the syntax-directed derivation holds with the usage environment $\Sv$ instead of the originally provided environment $\E$. Indeed,
$\E$ does not contain suspended and borrow bindings, since those
are discovered on the fly and recorded in $\Sv$.

>>>>

\begin{theorem}[Soundness of inference]
  Given a type environment $\E$ containing only value bindings,
  $\E|_\tau$ containing only type binding and a term $e$,\\
  if $\inferW{\Sv}{(C,\unif)}{\E;\E_\tau}{e}{\tau}$
  then $\inferS{C}{\unif(\Sv;\E_\tau)}{e}{\tau}$, $\unif C = C$ and $\unif \tau = \tau$
\end{theorem}

The syntax-directed derivation holds with the usage environment $\Sv$ instead of the originally provided environment $\E$. Indeed,
$\E$ does not contain suspended and borrow bindings, since those
are discovered on the fly and recorded in $\Sv$. The type binding, however,
are directly taken from the syntax-directed derivation.
